Primate Cognition and the Red Queen Hypothesis

### 2021-05-23 Article/Article.Rmd

bibliography: bibliographyarticlepackage.bib
csl: science.csl
#biblio-style: apa

@@

#Just to see the difference as pinpointed by the warning
# geosphere::areaPolygon(areaTransitory)
# gArea(areaTransitory)
# really false
# geosphere::centroid(areaTransitory)
# gCentroid(areaTransitory)
#ok

layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)

####
## Fig interaction
####

#Import data
summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)

#Tree
tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")

#Create geography df
geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
colnames(geoBinary) <- c("SpeciesPhylo", "Loc")

#Create species ID
hc = as.hclust(tree)#bird.orders)
labels = hc$labels  # name of birds

labels.tordc <- as.data.frame(labels)
colnames(labels.tordc) <- "Name"
labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")

labels.rdc <- apply(labels.tordc, 1, function(x){
  if(!is.na(x[3])){
    paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
  } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
  }
}
)

#Match to have right order for geography
locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
colLoc <- colourArea

#Match to have diet
dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]

#Getting species labels abbreviated
speciesLabels <- hc$labels#Should be in the tree order

#Create the circos plot linking species based on their diet and geography
circos.clear()
circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
circos.initialize(speciesLabels, xlim = c(0, 1))

#Species name + area it belongs to
circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
             panel.fun = function(x, y) {
               i=CELL_META$sector.numeric.index
               circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0), 
                           facing = "clockwise", niceFacing = TRUE,
                           col = "black", cex = 0.35, font=3)

              geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
              for(g in 1:length(geo)){
                if(geo[g]==1){
                  #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
                  circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
                }
              }
             })

#Plot the geographic links
for(i in 1:length(speciesLabels)){
  #locI <- which(strsplit(locationSpecies[i], "")==1)
  for(j in i:length(speciesLabels)){
    #locJ <- which(strsplit(locationSpecies[j], "")==1)
    product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
    if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
      #Do nothing
    }
    else{
      if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
        # colour <- as.data.frame(table(colLoc[which(product==1)]))
        # if(is.finite(max(colour$Freq))){
        # }else{
        #   print(c(i,j))
        # }
        # colour <- colour[colour$Freq==max(colour$Freq),1][1]
        circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col="lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
      }
      else{
        #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
      }
    }
  }
}
circos.clear()

#Plot the phylogenetic tree in a new circular plot
n = length(labels)  # number of species
dend = as.dendrogram(hc)

par(new = TRUE) # <- magic
circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
circos.initialize("a", xlim = c(0, n)) # only one sector
# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3, 
#              panel.fun = function(x, y) {
#                for(i in seq_len(n)) {
#                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5), 
#                              facing = "clockwise", niceFacing = TRUE,
#                              col = "black", cex = 0.2, font=3)
#                }
#              })

#suppressPackageStartupMessages(library(dendextend))
#dend = color_branches(dend, k = 6, col = 1:6)
dend_height = attr(dend, "height")
circos.track(ylim = c(0, dend_height), bg.border = NA,
             track.height = 0.95, panel.fun = function(x, y) {
               circos.dendrogram(dend)
             })
circos.clear()

####
## Fig map
####

#Create the map of the geographic area
#Have background
maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA)#, ylim=c(-60, 50))

# addLabel(x=0.05, y=0.075, label="A", radius=7, circle=TRUE, circle.bg="black", font.col="white")
#

for(i in 1:length(areaName)){
  plot(get(paste("area", i, sep="_")), col=colourArea[i], border=colourArea[i], add=TRUE) #border="black",
}
#Have borders
#plot(worldMap, col=NA, border="white",bg="white", lwd=0.1, add=TRUE)
# for(i in 1:length(areaName)){
#   plot(get(paste("area", i, sep="_")), col=NA, border="black",  add=TRUE)
# }
points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.15)
points(x=centroid[,1], y=centroid[,2], cex=1.15, col=c("white", "white", rep("black", times=10)))
text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.4, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))

@@

library(RColorBrewer)
colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")

###
## Fig brain values / circular
###

summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Brain
summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Brain
summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Brain
summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Brain
summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Brain

#Brain data
relativeValueEQ <- summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)] - 1#runif(length(speciesLabels), -1, 1)
relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])

library(circlize)
circos.clear()
circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
circos.initialize(speciesLabels, xlim = c(0, 1))

#Species name
circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
             panel.fun = function(x, y) {
               i=CELL_META$sector.numeric.index
               circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
                           facing = "clockwise", niceFacing = TRUE,
                           col = "black", cex = 0.35, font=3)
             })

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
}, track.height = 1/15)

#Background
circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
}, track.height = 1/15)

circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
  circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
}, track.height = 1/15)

library(plotrix)
#Main circle
for(i in 1:13){
  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
}

#increment of 0.5
for(i in 1:26){
  draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
}

#Value

#EQ
absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueEQ[i])){}  else{
    if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
    }
    else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueEQ[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
    }
    else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
    }
    else{}
  }
}, track.height = 0.1)

#Striatum
absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
  if(is.na(relativeValueStriatum[i])){}  else{
    if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
    }
    else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
    }
    else{}
  }
}, track.height = 0.1)

circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
  i=CELL_META$sector.numeric.index
  if(is.na(relativeValueStriatum[i])){}  else{
    #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
    if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
    }
    else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
      circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
      circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
    }
    else{}
  }
}, track.height = 0.1)

>>>>

bibliography: bibliographyarticlepackage.bib
csl: science.csl
#biblio-style: apa
always_allow_html: true

@@

# #Just to see the difference as pinpointed by the warning
# # geosphere::areaPolygon(areaTransitory)
# # gArea(areaTransitory)
# # really false
# # geosphere::centroid(areaTransitory)
# # gCentroid(areaTransitory)
# #ok
# 
# layout(mat=t(c(1,2)), widths=c(40,40), heights=c(40))
# par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
# 
# ####
# ## Fig interaction
# ####
# 
# #Import data
# summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)
# 
# #Tree
# tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
# 
# #Create geography df
# geoBinary <- as.data.frame(summaryDataForPlot[,c(3,which(colnames(summaryDataForPlot)=="geographicCode"))])
# colnames(geoBinary) <- c("SpeciesPhylo", "Loc")
# 
# #Create species ID
# hc = as.hclust(tree)#bird.orders)
# labels = hc$labels  # name of birds
# 
# labels.tordc <- as.data.frame(labels)
# colnames(labels.tordc) <- "Name"
# labels.tordc <- separate(labels.tordc, col="Name", into=c("Name1", "Name2", "Name3"), sep="_")
# 
# labels.rdc <- apply(labels.tordc, 1, function(x){
#   if(!is.na(x[3])){
#     paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), ". ", substr(x[3], 1, 1), ".", sep="")
#   } else{paste(toupper(substr(x[1], 1, 1)), ". ", substr(x[2], 1, 3), sep="")
#   }
# }
# )
# 
# #Match to have right order for geography
# locationSpecies <- geoBinary$Loc[match(labels, geoBinary$SpeciesPhylo)]
# colLoc <- colourArea
# 
# #Match to have diet
# dietSpecies <- summaryDataForPlot$DietaryGuild[match(labels, summaryDataForPlot$SpeciesForPhylogeny)]
# 
# #Getting species labels abbreviated
# speciesLabels <- hc$labels#Should be in the tree order
# 
# #Create the circos plot linking species based on their diet and geography
# circos.clear()
# circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin = c(0, 0), "canvas.xlim" = c(-1.1, 1.1), "canvas.ylim" = c(-1.1, 1.1))
# circos.initialize(speciesLabels, xlim = c(0, 1))
# 
# #Species name + area it belongs to
# circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.1, track.margin=c(0.01, 0.01),
#              panel.fun = function(x, y) {
#                i=CELL_META$sector.numeric.index
#                circos.text(CELL_META$xcenter, 1, labels.rdc[i], adj = c(0, 0), 
#                            facing = "clockwise", niceFacing = TRUE,
#                            col = "black", cex = 0.35, font=3)
#                
#               geo <- as.numcharac(unlist(strsplit(locationSpecies[i], "")))
#               for(g in 1:length(geo)){
#                 if(geo[g]==1){
#                   #circos.points(CELL_META$xcenter,0.75/length(geo)*(2*g-1)/2, col=as.character(colLoc[g]), pch=19, cex=0.2)
#                   circos.rect(CELL_META$cell.xlim[1],0.75/length(geo)*(g-1), CELL_META$cell.xlim[2], 0.75/length(geo)*(g), col=as.character(colLoc[g]), border=NA)
#                 }
#               }
#              })
# 
# #Plot the geographic links
# for(i in 1:length(speciesLabels)){
#   #locI <- which(strsplit(locationSpecies[i], "")==1)
#   for(j in i:length(speciesLabels)){
#     #locJ <- which(strsplit(locationSpecies[j], "")==1)
#     product <- as.numcharac(unlist(strsplit(locationSpecies[j], "")))*as.numcharac(unlist(strsplit(locationSpecies[i], "")))
#     if(i==j|(length(unique(product))==1&unique(product)[1]==0)){
#       #Do nothing
#     }
#     else{
#       if(dietSpecies[i]=="Fruit"&dietSpecies[i]==dietSpecies[j]){
#         # colour <- as.data.frame(table(colLoc[which(product==1)]))
#         # if(is.finite(max(colour$Freq))){
#         # }else{
#         #   print(c(i,j))
#         # }
#         # colour <- colour[colour$Freq==max(colour$Freq),1][1]
#         circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=0.2, col="lightgray")#adjustcolor(as.character(colour), alpha.f=0.9))
#       }
#       else{
#         #circos.link(speciesLabels[i], runif(1, 0, 1), speciesLabels[j], runif(1, 0, 1), lwd=1, col="lightgray")
#       }
#     }
#   }
# }
# circos.clear()
# 
# #Plot the phylogenetic tree in a new circular plot
# n = length(labels)  # number of species
# dend = as.dendrogram(hc)
# 
# par(new = TRUE) # <- magic
# circos.par("canvas.xlim" = c(-1.05, 1.05), "canvas.ylim" = c(-1.25, 1.25))
# circos.initialize("a", xlim = c(0, n)) # only one sector
# # circos.track(ylim = c(0, 1), bg.border = NA, track.height = 0.3, 
# #              panel.fun = function(x, y) {
# #                for(i in seq_len(n)) {
# #                  circos.text(i-0.5, 0, labels.rdc[i], adj = c(0, 0.5), 
# #                              facing = "clockwise", niceFacing = TRUE,
# #                              col = "black", cex = 0.2, font=3)
# #                }
# #              })
# 
# 
# #suppressPackageStartupMessages(library(dendextend))
# #dend = color_branches(dend, k = 6, col = 1:6)
# dend_height = attr(dend, "height")
# circos.track(ylim = c(0, dend_height), bg.border = NA,
#              track.height = 0.95, panel.fun = function(x, y) {
#                circos.dendrogram(dend)
#              })
# circos.clear()
# 
# ####
# ## Fig map
# ####
# 
# #Create the map of the geographic area
# #Have background
# maps::map("world", fill=TRUE, col="lightgray", bg="white", border=NA)#, ylim=c(-60, 50))
# 
# # addLabel(x=0.05, y=0.075, label="A", radius=7, circle=TRUE, circle.bg="black", font.col="white")
# # 
# 
# for(i in 1:length(areaName)){
#   plot(get(paste("area", i, sep="_")), col=colourArea[i], border=colourArea[i], add=TRUE) #border="black",
# }
# #Have borders
# #plot(worldMap, col=NA, border="white",bg="white", lwd=0.1, add=TRUE)
# # for(i in 1:length(areaName)){
# #   plot(get(paste("area", i, sep="_")), col=NA, border="black",  add=TRUE)
# # }
# points(x=centroid[,1], y=centroid[,2], pch=19, col=c(colourArea[1], colourArea[2], rep("white", times=10)), cex=1.15)
# points(x=centroid[,1], y=centroid[,2], cex=1.15, col=c("white", "white", rep("black", times=10)))
# text(x=centroid[,1], y=centroid[,2], labels=1:length(areaName), cex=0.4, col=c("white", "white", rep("black", times=10)), adj=c(0.5,0.5))

@@

# library(RColorBrewer)
# colourVector <- c("darkgrey", brewer.pal(n = 5, name = "Set1")[1:5])
# colourVectorbis <- c("lightgray", brewer.pal(n = 5, name = "Pastel1")[1:5])
# colour.circle.points <- c("black", "darkred", "darkblue", "darkgreen", "purple4", "orange4")
# 
# ###
# ## Fig brain values / circular
# ###
# 
# summaryDataForPlot$EQ <- summaryDataForPlot$Brain*1.036*(10**-3)/(0.085*summaryDataForPlot$Bodymass**0.775)
# summaryDataForPlot$ratioNeocortex <- summaryDataForPlot$Neocortex/summaryDataForPlot$Brain
# summaryDataForPlot$ratioHippocampus <- summaryDataForPlot$Hippocampus/summaryDataForPlot$Brain
# summaryDataForPlot$ratioCerebellum <- summaryDataForPlot$Cerebellum/summaryDataForPlot$Brain
# summaryDataForPlot$ratioStriatum <- summaryDataForPlot$Striatum/summaryDataForPlot$Brain
# summaryDataForPlot$ratioMOB <- summaryDataForPlot$MOB/summaryDataForPlot$Brain
# 
# #Brain data
# relativeValueEQ <- summaryDataForPlot$EQ[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)] - 1#runif(length(speciesLabels), -1, 1)
# relativeValueNeocortex <- scale(summaryDataForPlot$ratioNeocortex[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
# relativeValueHippocampus <- scale(summaryDataForPlot$ratioHippocampus[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
# relativeValueCerebellum <- scale(summaryDataForPlot$ratioCerebellum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
# relativeValueStriatum <- scale(summaryDataForPlot$ratioStriatum[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
# relativeValueMOB <- scale(summaryDataForPlot$ratioMOB[match(speciesLabels, summaryDataForPlot$SpeciesForPhylogeny)])
# 
# 
# library(circlize)
# circos.clear()
# circos.par(gap.degree=0, gap.after=0, cell.padding=c(0,0,0,0), track.margin=c(0, 0))
# circos.initialize(speciesLabels, xlim = c(0, 1))
# 
# #Species name
# circos.track(ylim = c(0, 20), bg.border = NA, track.height = 0.05, track.margin=c(0.01, 0.1),
#              panel.fun = function(x, y) {
#                i=CELL_META$sector.numeric.index
#                circos.text(CELL_META$xcenter, 0, labels.rdc[i], adj = c(0, 0),
#                            facing = "clockwise", niceFacing = TRUE,
#                            col = "black", cex = 0.35, font=3)
#              })
# 
# #Background
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVector[1], border=colourVector[1])
# }, track.height = 1/15)
# 
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVectorbis[1], border=colourVectorbis[1])
# }, track.height = 1/15)
# 
# #Background
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVector[2], border=colourVector[2])
# }, track.height = 1/15)
# 
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVectorbis[2], border=colourVectorbis[2])
# }, track.height = 1/15)
# 
# #Background
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVector[3], border=colourVector[3])
# }, track.height = 1/15)
# 
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVectorbis[3], border=colourVectorbis[3])
# }, track.height = 1/15)
# 
# #Background
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVector[4], border=colourVector[4])
# }, track.height = 1/15)
# 
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVectorbis[4], border=colourVectorbis[4])
# }, track.height = 1/15)
# 
# #Background
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVector[5], border=colourVector[5])
# }, track.height = 1/15)
# 
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVectorbis[5], border=colourVectorbis[5])
# }, track.height = 1/15)
# 
# #Background
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVector[6], border=colourVector[6])
# }, track.height = 1/15)
# 
# circos.track(ylim = c(0, 1), bg.border = NA, panel.fun = function(x, y) {
#   circos.rect(0, 0, 1, 1, col=colourVectorbis[6], border=colourVectorbis[6])
# }, track.height = 1/15)
# 
# 
# library(plotrix)
# #Main circle
# for(i in 1:13){
#   draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15, col=NA, border="white")
# }
# 
# #increment of 0.5
# for(i in 1:26){
#   draw.circle(x=0,y=0,0.91-1/15-(i-1)*1/15/2, col=NA, border="white", lty=2)
# }
# 
# #Value
# 
# 
# 
# #EQ
# absMax <- max(abs(relativeValueEQ), na.rm=TRUE)
# circos.track(ylim = c(0, 1), bg.border = NA, track.index=2, panel.fun = function(x, y) {
#   i=CELL_META$sector.numeric.index
#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
#   if(is.na(relativeValueEQ[i])){}  else{
#     if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Fruit"){
#       circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
#     }
#     else if(relativeValueEQ[i] > 0 & dietSpecies[i]=="Leaf"){
#       circos.points(CELL_META$xcenter, relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
#     }
#     else{}
#   }
# }, track.height = 0.1)
# 
# 
# circos.track(ylim = c(0, 1), bg.border = NA, track.index=3,  panel.fun = function(x, y) {
#   i=CELL_META$sector.numeric.index
#   if(is.na(relativeValueEQ[i])){}  else{
#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
#     if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Fruit"){
#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
#       circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=19, col=colour.circle.points[1], cex=0.7)
#     }
#     else if(relativeValueEQ[i] <= 0 & dietSpecies[i]=="Leaf"){
#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, col=colour.circle.points[1], lty=3)
#       circos.points(CELL_META$xcenter, 1 + relativeValueEQ[i]/absMax, pch=21, col=colour.circle.points[1], bg="white", cex=0.7)
#     }
#     else{}
#   }
# }, track.height = 0.1)
# 
# 
# #Striatum
# absMax <- max(abs(relativeValueStriatum), na.rm=TRUE)
# circos.track(ylim = c(0, 1), bg.border = NA, track.index=4, panel.fun = function(x, y) {
#   i=CELL_META$sector.numeric.index
#   #circos.rect(0, 0, 1, 1, col=colourPositive, border=colourPositive)
#   if(is.na(relativeValueStriatum[i])){}  else{
#     if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Fruit"){
#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
#       circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
#     }
#     else if(relativeValueStriatum[i] > 0 & dietSpecies[i]=="Leaf"){
#       circos.segments(CELL_META$xcenter, 0, CELL_META$xcenter, relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
#       circos.points(CELL_META$xcenter, relativeValueStriatum[i]/absMax, pch=21, col=colour.circle.points[2], bg="white", cex=0.65)
#     }
#     else{}
#   }
# }, track.height = 0.1)
# 
# 
# circos.track(ylim = c(0, 1), bg.border = NA, track.index=5,  panel.fun = function(x, y) {
#   i=CELL_META$sector.numeric.index
#   if(is.na(relativeValueStriatum[i])){}  else{
#     #circos.rect(0, 0, 1, 1, col=colourNegative, border=colourNegative)
#     if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Fruit"){
#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
#       circos.points(CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, pch=19, col=colour.circle.points[2], cex=0.65)
#     }
#     else if(relativeValueStriatum[i] <= 0 & dietSpecies[i]=="Leaf"){
#       circos.segments(CELL_META$xcenter, 1, CELL_META$xcenter, 1 + relativeValueStriatum[i]/absMax, col=colour.circle.points[2], lty=3)
